timesliced_random_cell_selection

### 2018-11-02 src/raster_sjl.Rmd
working towards depth layer selection....

```{r}
nc <-  "./data/env/netcdf/1993_01_salinity.nc" # change the file path to where ever your netcdfs are saved
rasbr <- brick(nc,lvar = 4) #lvar = 4 is used because the netCDF contains four dimensions. Without this command, the raster brick will only have one level (the top one, which is my surface data)
rasbr # this will give you some information about the raster brick
```
We no longer care that the data originated from a netCDF file. Everything now is done with the raster brick.

@@

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/bio/observations.csv") #change this path to your .csv location
head(obs)
```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

>>>>

```{r}
nc <-  "../data/env/netcdf/1993_01_salinity.nc" # change the file path to where ever your netcdfs are saved
rasbr <- brick(nc,lvar = 4) #lvar = 4 is used because the netCDF contains four dimensions. Without this command, the raster brick will only have one level (the top one, which is my surface data)
rasbr # this will give you some information about the raster brick
```

We no longer care that the data originated from a netCDF file. Everything now is done with the raster brick.

@@

The next piece of data we need is the observation data itself. I've sent you the observations.csv in the email with this code.
```{r}
obs <- read.csv("../data/observations3.csv") #change this path to your .csv location
head(obs)
```
A note about obs$depth. This is not a measurement, but relates to the layer in the raster bricks. E.G. the observation in row one was found at rasbr[[15]], the observation in row 3 at rasbr[[17]]. I created this field myself.

@@

#shawn code

SL I AM DOING SOME STUFF HERE :O) 
THE ABOVE EXTRACTION IS THE HOOK UP. I WANT TO EXTRACT FOR A CERTAIN DEPTH DEFINED BY OBSSP IN ORDER TO AUTOMATE THIS. THIS MEANS YOU NEED
TO MAKE [[]] LINKED TO DEPTH...LET'S SEE IF WE CAN DO THIS NOW.
```{r}
obssp$salinity2 <- extract(x=rasbr_aea[[obssp$depth]], y = obssp)
obssp$salinity2 # just to take a look at the output
```

Ok, the above is close but not right. It is printing salinity for depths 15, 22, 17, 18, 15, 16, 16 for each observation record.
At least this is what I think. Let's check it out.
```{r}
obssp$salinity22 <- extract(x=rasbr_aea[[22]], y = obssp) #I expect this to be 33.42. Yep.
obssp$salinity22
```

Starting over now I have created a smaller observation file with only 3 records. 
Gonna create a loop here and iterate over the depths listed in the observation file
```{r}
Data_Loop <-NULL #Gonna put my loop data in here
for (i in obssp$depth) { #cycle through values in depth column (15, 22, 17)
  #this is the equation you will be calculating for every value of y
  sal <- extract(x=rasbr_aea[[i]], y = obssp) #create a data list

  #Put your data in a data frame. Don't forget to enclose this within the loop!
  Data_Loop <- rbind(Data_Loop, data.frame(depth=i, year=obssp$year, month=obssp$month, lon=obssp$lon, lat=obssp$lat, Salinity=sal))

  #print the i value so you can track progress. Good for longer loops
  print(i)
  #Close the loop
  }
Data_Loop
```

SL: TRY IT ANOTHER WAY. Problem is that we need to tell x to be at specific depth as specified by obssp$depth and y to be only the lat and lon at that depth.
The two examples here (one above and one below) are VERY close. Just a matter of tweaking and playing around a bit more. See if you can figure it out.
```{r}
Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) { #cycle through values in depth column (15, 22, 17) #NO IT CYCLES THROUGH THE ROWS
  #this is the equation you will be calculating for every value of y
  sal <- extract(x=rasbr_aea[[obssp$depth[i]]], y = obssp[i,]) #go with i row in obssp

  #Put your data in a data frame. Don't forget to enclose this within the loop!
  Data_Loop <- rbind(Data_Loop, data.frame(depth=obssp$depth, year=obssp$year, month=obssp$month, lon=obssp$lon, lat=obssp$lat, Salinity=sal))

  #print the i value so you can track progress. Good for longer loops
  print(i)
  #Close the loop
}
Data_Loop
```

# sam tests on shawns loop

let's get the values manually
```{r}
test15 <- extract(x=rasbr_aea[[15]], y = obssp)
test22 <- extract(x=rasbr_aea[[22]], y = obssp)
test17 <- extract(x=rasbr_aea[[17]], y = obssp)
test17
```

this loop replaces the values in obssp$samtest with the last depth layer... ie. the process does not work for each row in obssp in turn
```{r}
Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  print(de)
  obssp$samtest <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y

  #Put your data in a data frame. Don't forget to enclose this within the loop!
  #Data_Loop <- rbind(Data_Loop, data.frame(depth=obssp$depth, year=obssp$year, month=obssp$month, lon=obssp$lon, lat=obssp$lat, Salinity=sal))

  #print the i value so you can track progress. Good for longer loops
  #print(i)
  #Close the loop
}
#Data_Loop
obssp$samtest
```

take 2
```{r}
Data_Loop <-NULL #Gonna put my loop data in here
for (i in 1:length(obssp)) {  # CYCLES THROUGH THE ROWS
  de <- obssp$depth[[i]]  #have a variable for the depth layer
  print(de)
  obssp$samtest <- extract(x=rasbr_aea[[de]], y = obssp) #this is the equation you will be calculating for every value of y

  #Put your data in a data frame. Don't forget to enclose this within the loop!
  #Data_Loop <- rbind(Data_Loop, data.frame(depth=obssp$depth, year=obssp$year, month=obssp$month, lon=obssp$lon, lat=obssp$lat, Salinity=sal))

  #print the i value so you can track progress. Good for longer loops
  #print(i)
  #Close the loop
}
#Data_Loop
obssp$samtest
```
